\fontsize{14}{14}Bachelor Thesis \\ in \\Allgemeine Informatik \fontsize{22}{22}\textbf{Transhumanism}\\ \fontsize{18}{18} The New Human

### 2014-01-13 draft.tex
More changes

% Author and supervisor
\begin{tabular}{l l}
	 Referent:  & Hr. Burzlaff \\
	 Korreferent: & N/A\\
	 Vorgelegt am: & \today\\ % TODO: Put date
	 Vorgelegt von: & Marcel M\"ueller\\
	 & [Matrikelnummer] \\
	 & [Strasse und Hausnummer] \\
	 & [PLZ und Stadt] \\
	 & [HFU-Emailadresse]\\
\end{tabular}

@@

        This solution is not ideal either.

@@

        That is, many different Limb Modifications could appear on a sort of global market, bringing you features you did not posses before hand. 

@@

        And why not cook it directly through your hands? Or get by with solid food all the way?

@@

        As the final advancement, the ability to replace the whole body would allow for a complete revolution of the human status. 

@@

        Once our understanding is far enough we might even replace the sick Pancreas completely.

@@

        But we would not have to stop at our own bodies and also monitor our environments. 
        So workers that have to work in hazardous environments could have integrated Geiger Counters in their Eyes, allowing them to view disintegrations in real time. 

@@

        This realization is core to the Transhumanist. 
        Since transcending the Human body is one of the goals most aspire to. 

@@

        Those familiar with Physolophical concepts about the human existence know that there are many currents of thought. 

@@

	      Now let's imagine that in the near future your mind would be scanned. All of your memories and special connections would be mapped and uploaded to a central computer. Then, taking state of the art transmission this state of yourself would be send to a far away planet. There your mind could then be put into a robot. You would have a new body as the one on earth would have been destroyed. Taking the previous points, in (2. + 3.) you would still be you. After all, your consciousness still exists and only your old body got merely destroyed. After (1.) you would be dead. This consciousness in the robot would be another being. You had left your body behind, thus you had allowed to be killed. This Robot is a different being altogether, which might die as well once it is destroyed.

@@

  \section{The Moral standpoint}
    \subsection{Money = Better technology}

@@

      \end{par}
    \subsection{Old People = Rigid Societies}
      \begin{par}

	      Explain how old people in positions of power can be bad in the long run.

      \end{par}
  \subsection{Immortality and Crimes?}
    \begin{par}

	    Explain how Immortality can affect crimes and their punishments.

    \end{par}
  \section{Human Standpoint}
    \subsection{Singularity = No more thinking?}
      \begin{par}

	      Explain how a super intelligent Computer could be the source of problems in the world.

      \end{par}
    \subsection{Immortality = No Natural Evolution}
      \begin{par}

@@

>>>>

% Author and supervisor
\begin{tabular}{l l}
   Referent:  & Hr. Burzlaff \\
   Korreferent: & N/A\\
   Vorgelegt am: & \today\\ % TODO: Put date
   Vorgelegt von: & Marcel M\"uller\\
   & [Matrikelnummer] \\
   & [Strasse und Hausnummer] \\
   & [PLZ und Stadt] \\
   & [HFU-Emailadresse]\\
\end{tabular}

@@

        This solution is not ideal.

@@

        That is, many different Limb Modifications could appear on a sort of global market, bringing you features you did not posses beforehand. 

@@

        And why not cook it directly through your hands? Or get by with solid food all together?

@@

        It is the final advancement, the ability to replace the whole body that would allow for a complete revolution of the human status. 

@@

        Once our understanding is far enough we might even replace the sick Pancreas completely thus curing many health problems that exist throughout the world today.

@@

        But we would not have to stop at our own bodies but also monitor our environments. 
        For example workers that have to work in hazardous environments could have integrated Geiger Counters in their Eyes, allowing them to view disintegrations in real time. 

@@

        This realization is core to the Transhumanist Thought since transcending the Human body is one of the goals most aspire to. 

@@

        Those familiar with Physolophical concepts about the human existence know that there are many currents of thought about the idea of what one might call the mind. 

@@

        Now let's imagine that in the near future your mind would be scanned. 
        All of your memories and special connections would be mapped and uploaded to a central computer. 
        Then, taking state of the art transmission this state of yourself would be send to a far away planet. 
        There your mind could then be put into a robot. You would have a new body as the one on earth would have been destroyed. 
        Taking the previous points, in (2. + 3.) you would still be you. After all, your consciousness still exists and only your old body got merely destroyed. 
        After (1.) you would be dead. This consciousness in the robot would be another being. 
        You had left your body behind, thus you have allowed to be killed. 
        This Robot is a different being altogether, which might die as well once it is destroyed.

@@

  \section{The possible effects}
    \subsection{The Impact of Money}

@@

      \end{par}
      \begin{par}
        Medication is expensive. It takes decades of research and testing before it gets approved to be used on humans. 
        Along the way it could fail to pass a critical percentage and get rejected.
        With a financial term it could be labeled as \emph{risky}.
        This same process applies to prostethics as well today, and insurance does not always provide full coverage -- leaving the lesser wealthy behind.
      \end{par}
      \begin{par}
        There is no reason to believe that augmentations of the human body would be treated any differently, if anything it might be even worse as most might not be labeled as critical for a good health.
        It is a known theory that more privileged citizens have a tendency to attribute their wealth to their own actions.\cite{MoneyMean} 
        Using augments this could be further entrenched and even marginalize parts the society even more.
        One could imagine a dichotomy between people who have been \emph{augmented} and those who have not solely due to their upbringing.
      \end{par}
  \subsection{The Impact on Crimes}
    \begin{par}
      Committing a crime in the society of today is often going to result into prison.
      But will the punishments of today still be appropriate if our Lifespans triple?
      One could easily imagine someone stealing a particulary large amount of money and receives a jail term of a year.
      If the projected lifespan is about four hundred years, one year is an incredibly small time and might seem misappropriate.
    \end{par}
    \begin{par}
      This stand point is also valid from the other side. If you are sentenced to life and still have two hundred years to life is it still appropriate?
      In today's society the death sentence is a very polemic subject, it might resurface at that point.
    \end{par}
    \subsection{The Impact of Immortality}
      \begin{par}

@@

      \end{par}
      \begin{par}
        Genetic Engineering is being actively today.
        Today the biggest goal of it is therapeutic applications. 
        There are many genetic diseases and we do not understand them all.
        However once we truly understand our genome it is very possible that we, as a human race, can evolve ourselves.
      \end{par}
      \begin{par}
        This self evolution could lead to brains that are more performant, have a higher memory capacity and might be less prone to diseases.
        A higher athletic condition is also possible by activating or substituting some genes at specific conditions.
      \end{par}
  \section{To Resume}
    \being{par}
      Transhumanism incorporates our current technical advancement and tries to apply it to our own species. 
      Imagining what is possible today and what could be tomorrow.
      This process of trying to make sense of what does not exist yet is fundamental in how we approach science as it allows us to work towards a goal and thus get progress.
